---
title: "Practice Assignment"
author: "Jenn Ji"
date: "January 7, 2018"
output: 
  html_document: 
    keep_md: yes
---
```{r setup, include = FALSE}
library(tidyverse)
```

### Passenger Breakdown
```{r, echo = FALSE}
tf = data.frame(Titanic) #turn dataset into dataframe
Nchildren = 
  tf %>% #pipe function used to chain several operations on dataset "tf"
  subset(Age =="Child") %>% #subsetting "tf" by Age = child
  summarize(sum(Freq)) #sum of the frequency returns number of child 
Nadults = 
  tf %>%
  subset(Age=="Adult") %>%
  summarize(sum(Freq))
NFemale = 
  tf %>%
  subset(Sex=="Female") %>%
  summarize(sum(Freq))
NMale = 
  tf %>%
  subset(Sex == "Male") %>%
  summarize(sum(Freq))
```

There were `r Nchildren` children on the titianic 
There were `r Nadults` adults on the titanic

There were `r NFemale` females and `r NMale` males on the Titanic.Therefore, there were more males than females on the Titanic.

### Survival based on age 
```{r, echo = FALSE}
AliveC = 
  tf %>% #pipe function used to chain several operations on dataset "tf"
  subset(Age=="Child" & Survived=="Yes") %>% #subset data "tf" for children who have survived
  summarize(sum(Freq))
            
AliveA = 
  tf %>%
  subset(Age=="Adult" & Survived=="Yes") %>%
  summarize(sum(Freq)) 

Survchild = round(AliveC/Nchildren*100,digits=2)  #percentage of children survived, rounded to 2 decimal places
Survadult = round(AliveA/Nadults*100, digits=2)  
```

`r Survchild`% of children survived on the Titanic, whereas `r Survadult`% of adults survived.The children had a better survival rate compared to adults. 

### Survival based on class

The survival rate for each class is shown below:
```{r, echo = FALSE}
t1 =  #table 1
  tf %>%
  group_by(Class)%>% #group by class
  summarise("Total Number" = sum(Freq)) # generate table containing total number of passengers subset by class
t2 = #table 2
  tf %>%
  subset(Survived=="Yes") %>% #subset data to only contain survived passengers
  group_by(Class) %>% # Group by class
  summarize(Survived = sum(Freq)) # generate table containing survived number of passengers by class

t3 = merge(t2,t1,by="Class") #merge tables 1 and 2, keep first column - Class
tf2 = data.frame(t3) #turn table into dataframe

tf2$"Survival rate" <- round(tf2$Survived/tf2$Total.Number*100,digits=2) # add an column named survival rate containing the rate of survival to 2 decimal places (Survived/total number)

knitr::kable(tf2) #print this table when Knitted
```

As shown by above table, first class had the highest survival rate.

### Data Visualization
